The problem and promise of scale in multilayer animal social networks

### 2020-02-14 paper/manuscript.Rmd
reflow

## Habitat selection and space use
<!-- TODO: Gerard ‘openness’ paper -->
Social structure and habitat selection are intimately
linked: individuals must share space to interact and the distribution of
resources influences group dynamics and home range size [@Webber_2018].
Social structure is influenced by resource availability and seasonality
[@Peignier_2019], configuration [@He_2019] and fragmentation [@Banks_2007].
Habitat selection, the disproportionate use of available resources or landscape
features by animals [@Manly_1993; @Boyce_1999], is a scale-dependent process
[@Mayor_2009]. Multilayer networks represent a novel framework for considering the influence of habitat selection and space use on sociality across scales.

<!--Animals select habitats at multiple scales ... (Mayor)  Mayor scale -->

<!-- McGarigal 2016 organisms select habitat at multiple scales, temporal spatial
should investigate scale dependency. linking ecological processes to scale eg foraging or predator-prey dynamics

Mayor 2007 - scale paper
MRSF Laforge paper 
van Beest et al. 2014 scale paper 
Habitat–performance relationships: finding the right metric at a given spatial scale
Multi-scale habitat selection modeling: a review and outlook
-->

>>>>

## Habitat selection and space use
Social structure and habitat selection are intimately linked: individuals must
share space to interact and the distribution of resources influences group
dynamics and home range size [@Webber_2018]. Social structure is influenced by
resource availability and seasonality [@Peignier_2019], configuration [@He_2019]
and fragmentation [@Banks_2007]. Habitat selection, the disproportionate use of
available resources or landscape features by animals [@Manly_1993; @Boyce_1999],
is a scale-dependent process [@Mayor_2009]. Multilayer networks represent a
novel framework for considering the influence of habitat selection and space use
on sociality across scales.

<!-- 
TODO: Gerard ‘openness’ paper

McGarigal 2016 organisms select habitat at multiple scales, temporal spatial
should investigate scale dependency. linking ecological processes to scale eg foraging or predator-prey dynamics

MRSF Laforge paper 
van Beest et al. 2014 scale paper 
Habitat–performance relationships: finding the right metric at a given spatial scale
Multi-scale habitat selection modeling: a review and outlook
-->
